### 2021-02-24 input/proposal.tex
reworkd algo a4

\TODO{Not so easy\ldots}

@@

This allows processes to quickly discard stale messages saving
bandwidth. For instance, a process that received a message originated
at Process $a$ with a version $2$ knows that any message originated at
Process $a$ with a version $1$ are stale system-wide; it must not
forward it. As consequence, vectors of versions also ensure
termination, for messages \TODO{add and del} cannot follow each other
in an infinite loop. In terms of traffic, this only requires each
\TODO{delete} message to piggyback a source identifier and version
number.

>>>>

To ease the reasoning about inter-AS dynamic partitioning in dynamic
networks, \NAME runs an independant broadcast protocol for each
object, and for each rank of links.  \TODO{Not so easy\ldots}
\TODO{Write and describe algo.} \TODO{Overhead of separating things,
  slightly more memory, but traffic wise? slower ?}  \TODO{In the
  example, not only Process $b$ keeps $e_1$ as its best partition, but
  it keeps it for links of rank 0, and links of rank 1.}

The rest of this section describes our proposal to solve these smaller
scientific problems. It first tackles dynamic partitions where
processes can add or delete partitions resulting in stale information
that may impair correctness. It then tackles dynamic networks where
edges appear and disappear at any time resulting in invalid
information that may impair correctness.

@@

This allows processes to quickly discard stale messages saving
bandwidth. For instance, a process that received a message originated
at Process $a$ with a version $2$ knows that any message originated at
Process $a$ with a version $1$ are stale system-wide; it must not
forward it. As consequence, vectors of versions also ensure
termination, for corresponding add and delete messages cannot follow
each other in an infinite loop. In terms of traffic, this only
requires each \TODO{delete} message to piggyback a source identifier
and version number.
